Designing Turk Experiments for Visual Statistical Inference

### 2013-04-18 paper_turk.tex
turk payment information updated

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{Majumder:2011}. It is better to get observers as diverse as possible without being much concerned about the observers formal training about statistical graphics.

Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments. The web site is very convenient and reliable to collect simple experiment data. But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work. So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design. The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}. The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site. This facilitates getting data directly in a local server.

@@

>>>>

Even though under some situation it is possible to obtain the power of visual inference theoretically \cite{Majumder:2011},  it is hard to obtain power explicitly with a mathematical formula since it is very much dependent on individual observation. One approach to estimate the power is to recruit observers to evaluate lineups obtained in known controlled situation \cite{Majumder:2011}. It is better to get observers as diverse as possible without being much concerned about the observers' formal training about statistical graphics.

Amazon Mechanical Turk web site \cite{turk} is a very good resource for recruiting reliable survey participants for visual experiments. This is the place where people come to work online and get paid. The web site is very convenient and reliable to collect simple experiment data. But to design a complex experiment like what we need using their web interface is a pain and often a very time consuming work. So, to run the turk experiment we felt the necessity for a well customized web site where the lineups presented to the observers could be easily controlled according to the experimental design. The work flow design of such a mechanism is shown in figure \ref{fig:turk_work_flow}. The plan is to forward turk workers to a well customized web site while payment could be processed from turk web site. This facilitates getting data directly in a local server.

@@

\begin{table}[hbtp]
\caption{Number of task submitted by the turk workers, number of task got rejected and total task completion time for each of the different experiment indicate the performance of turk workers. Majority of the tasks are rejected for boxplot experiment and the payment per task was the lowest for this experiment.}
\centering 
\begin{tabular}{clccccc} 
\hline
Experiment &  Plot & Submitted & Rejected & Duration & Pay/Task \\ %[0.5ex] % inserts table %heading 
\hline
1 & Boxplot & 406 & 106 & 527340 & 0.5\\
2 & Scatterplot & 359 & 9 & 153660 & 1\\
3 & Contaminated plot & 219 & 19 & 454200 & 1\\
4 & Polar vs Cartesian & 110 & 10 & 41940 &1\\
5 & Hist vs density & 234 & 37 & 149640 & 1\\
6 & Violine vs boxplot & 417 & 17 & 381120 &1 \\
7 & Group separation & 106 & 6 & 18540 &1\\
8 & Sine Illusion & 101 & 1 & 282180 &1\\
\hline
\end{tabular}
\label{tbl:worker_performance}
\end{table}

\begin{figure}[hbtp]
   \centering
       \scalebox{.6}{\includegraphics{rejected_task.pdf}}
       \caption{Percentage of rejected task for various experimental plot type.}
       \label{fig:rejected_task}
\end{figure}
